\LARGE \bf Grasp Metric for Shape Uncertainity with Gaussian Proccess Implicit Surface Representation (Not Finished Work)

### 2014-07-14 paper.tex
added stuff

\vspace{10pt}
 A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}. However, only recently have people started looking into a metric's robustness to uncertainty. Prior work by Zheng et al \cite{zheng2005}, looked at how to efficiently include uncertainty in friction coefficient and movement of gripper arm. However, they assumed a known surface of the object. In robotics today, where our objects are represented as noisy point clouds, shape uncertainty is a very common problem \cite{singhbigbird}.

@@

@@

 We also define the function level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide1.jpg}
\caption{Parameterized Line of Action along a Object}
\vspace*{-10pt}
\label{fig:line_of_action}
\end{figure}
\textbf{TODO:MORE DESCRIPTIVE GRAPHIC}
\subsection{Distribution on Contact Points} The probability distribution along the line $\gamma(t)$ is given by the following:

@@

This gives the distributions along the entire line of action in the workspace, however we want to compute the joint distribution   $p\big(\textbf{c}_i= \gamma(t)\big) = p\big(f(\gamma(t))=0, f(\gamma(\tau))> 0: \forall \tau \in [0,t)\big)$. Hence we want to know at a point what the distribution  is that it is at the surface and the probability that all points before are before the surface. points before it on line are on the surface as well, this avoids the problem of the distribution producing multiple modes for each intersection with the surface. We now derive a way to compute an upper-bound on this distribution

@@

 \begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| & =||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
                                      &+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
\end{align*}

>>>>

\vspace{10pt}
 A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.  In robotics today, where our objects are represented as noisy point clouds, shape uncertainty is a very common problem \cite{singhbigbird}. As shown in Fig. \ref{fig:noisy data}, the noise in object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.  However, only recently have people started looking into a metric's robustness to uncertainty. Prior work by Zheng et al \cite{zheng2005}, looked at how to efficiently include uncertainty in friction coefficient and movement of gripper arm. . However, they assumed a known surface of the object.

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide2.jpg}
\caption{An example of the noise from a Kinect Like Sensor}
\vspace*{-10pt}
\label{fig:noisy data}
\end{figure}

@@

 We also define the  level set function as $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ and an implicit surface as $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.

\begin{figure}[ht!]
\centering
\includegraphics[scale = 0.3]{figures/Slide1.jpg}
\caption{Parametrized Line of Action along a Object}
\vspace*{-10pt}
\label{fig:line_of_action}
\end{figure}
\textbf{TODO:MORE DESCRIPTIVE GRAPHIC}
\subsection{Distribution on Contact Points} The probability distribution along the line $\gamma(t)$ is given by the following:

@@

This gives the distributions along the entire line of action in the workspace, however we want to compute the joint distribution   $p\big(\textbf{c}_i= \gamma(t)\big) = p\big(f(\gamma(t))=0, f(\gamma(\tau))> 0: \forall \tau \in [0,t)\big)$. Hence we want to know at a point what the distribution  is that it is at the surface and the probability that all points before are before the surface, this avoids the problem of the distribution producing multiple modes for each intersection with the surface. We now derive a  this distribution

@@

 \begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| & \leq ||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||) + ||\Delta{\textbf{r}_{i,\zeta}}(\zeta)|| \\
                                      &+ \tau(||\Delta \textbf{n}_{i,\zeta}||(1+||\bar{\textbf{r}}_i||)+||\Delta \textbf{r}_{i,\zeta}||)
\end{align*}
